Supplemental Material for ``Assessing United States county-level exposure for research on tropical cyclones and human health"

### 2019-01-28 tables/metric_definitions.tex
Work some on formatting

\begin{table}%[tbhp] 
\centering 
\caption{Exposure metrics considered to assess county-level exposure to 
tropical cyclones}
\begin{tabular}{p{0.9cm}p{2.5cm}p{9cm}} 
Metric & Available & Criteria for exposure \\ \midrule 
Distance & 1988--2015 & County population mean center within 100 kilometers of storm track \\ 
Rain & 1988--2011 & County cumulative rainfall of 75 millimeters or more over the period from two days before to one day after the storm's closest approach and county population mean center within 500 kilometers of the storm track \\ 
Wind & 1988--2015 & Modeled maximum sustained wind speed at the county's population mean center 15 meters per second or higher during the storm\\ 
Flood & 1996--2015 & Flood event listed in the National Oceanic and Atmospheric Administration (NOAA) Storm Events database for the county with a start date within two days of the storm's closest approach and county population mean center within 500 kilometers of the storm track \\
Tornado & 1996--2015 & Tornado event listed in the NOAA Storm Events database for the county with a start date within two days of the storm's closest approach and county population mean center within 500 kilometers of the storm track\\
\bottomrule 
\end{tabular} 
\label{tab:exposuremetrics} 
\end{table}

>>>>

\begin{table}%[tbhp] 
\centering 
\caption{Exposure metrics considered to assess county-level exposure to 
tropical cyclones}
\begin{tabular}{p{0.9cm}p{2.5cm}p{9cm}} 
Metric & Available & Criteria for exposure \\ \midrule 
Distance & 1988\,--\,2015 & County population mean center within 100 kilometers of storm track \\ 
Rain & 1988\,--\,2011 & County cumulative rainfall of 75 millimeters or more over the period from two days before to one day after the storm's closest approach and county population mean center within 500 kilometers of the storm track \\ 
Wind & 1988\,--\,2015 & Modeled maximum sustained wind speed at the county's population mean center 15 meters per second or higher during the storm\\ 
Flood & 1996\,--\,2015 & Flood event listed in the National Oceanic and Atmospheric Administration (NOAA) Storm Events database for the county with a start date within two days of the storm's closest approach and county population mean center within 500 kilometers of the storm track \\
Tornado & 1996\,--\,2015 & Tornado event listed in the NOAA Storm Events database for the county with a start date within two days of the storm's closest approach and county population mean center within 500 kilometers of the storm track\\
\bottomrule 
\end{tabular} 
\label{tab:exposuremetrics} 
\end{table}

### 2019-01-28 tables/stormseverity.tex
Work some on formatting

% latex table generated in R 3.4.3 by xtable 1.8-2 package
% Wed Oct 10 12:11:35 2018
\begin{table}[ht]
\centering
\caption{Summary statistics for exposure metrics considered to assess county-level exposure to
         tropical cyclones. A county exposure represents the exposure of a specific eastern U.S.  
         county to a specific tropical cyclone. A county can be exposed to multiple tropical cyclones within
         a year, and a tropical cyclone can create multiple county exposures under a given metric.
         The median and interquartile range of county exposures per tropical cyclone is based on
         the tropical cyclones for which at least one U.S. county was exposed. The years for which
         data are available for each metric are given in Table 1.} 
\label{tab:exposuresummaries}
\begin{tabular}{p{1.75cm}p{3cm}p{4cm}p{4cm}}
  \toprule
Metric & Mean (interquartile range) of county exposures per year & Median (interquartile range) of county exposures per tropical cyclone & Tropical cyclone with most counties exposures (\# exposed counties) \\ 
  \midrule
Distance & 433 (224, 503) & 84 (23, 173) & Beryl, 1994 (330) \\ 
  Rain & 401 (152, 553) & 68 (14, 146) & Frances, 2004 (464) \\ 
  Wind & 224 (83, 353) & 34 (8, 80) & Ike, 2008 (355) \\ 
  Flood & 213 (84, 249) & 26 (6, 57) & Ivan, 2004 (317) \\ 
  Tornado & 53 (16, 43) & 7 (2, 16) & Ivan, 2004 (91) \\ 
   \bottomrule
\end{tabular}
\end{table}

>>>>

% latex table generated in R 3.4.3 by xtable 1.8-2 package
% Wed Oct 10 12:11:35 2018
\begin{table}[ht]
\centering
\caption{Summary statistics for exposure metrics considered to assess county-level exposure to
         tropical cyclones. A county exposure represents the exposure of a specific eastern US
         county to a specific tropical cyclone. A county can be exposed to multiple tropical cyclones within
         a year, and a tropical cyclone can create multiple county exposures under a given metric.
         The median and interquartile range of county exposures per tropical cyclone is based on
         the tropical cyclones for which at least one US county was exposed. The years for which
         data are available for each metric are given in Table 1.} 
\label{tab:exposuresummaries}
\begin{tabular}{p{1.75cm}p{3cm}p{4cm}p{4cm}}
  \toprule
Metric & Mean (interquartile range) of county exposures per year & Median (interquartile range) of county exposures per tropical cyclone & Tropical cyclone with most counties exposures (\# exposed counties) \\ 
  \midrule
Distance & 433 (224, 503) & 84 (23, 173) & Beryl, 1994 (330) \\ 
  Rain & 401 (152, 553) & 68 (14, 146) & Frances, 2004 (464) \\ 
  Wind & 224 (83, 353) & 34 (8, 80) & Ike, 2008 (355) \\ 
  Flood & 213 (84, 249) & 26 (6, 57) & Ivan, 2004 (317) \\ 
  Tornado & 53 (16, 43) & 7 (2, 16) & Ivan, 2004 (91) \\ 
   \bottomrule
\end{tabular}
\end{table}

### 2019-01-28 writing/anderson_ehp_supp.tex
Work some on formatting

\begin{figure}[tbhp!]
\centering
\includegraphics[width=0.7\linewidth]{hurrtracks}
\caption{Tracks of all tropical cyclones included in the study. The study
included all tracked storms in the revised Atlantic hurricane database
\ac{HURDAT2}~\citep{landsea2013} that came within 250~\si{\kilo\metre} of at least on
\ac{US} county, 1988\,--\,2015. Thicker lines show the tracks of storms whose
names were retired, indicating that the storm was particularly severe or had
notable impacts~\citep{retirednames}.}
\label{fig:hurrtracks}
\end{figure}

@@

\begin{figure}[tbhp!]
\centering
\includegraphics[width=\linewidth]{othertopstorms}
\caption{Counties exposed, based on different exposure metrics, to the storms
with largest extent (as measured by the number of counties exposed based on any
metric) from each of the clusters shown in the Jaccard heatmap in the main text
(Figure 2).}
\label{fig:othertopstorms}
\end{figure}

@@

\begin{figure}[tbhp!]
\centering
\includegraphics[width=\linewidth]{windexamples}
\caption{Wind classifications for the two storms, Hurricanes Sandy (2012) and
Ike (2008) for which exposure classifications from modeled wind
data~\citep{stormwindmodel} and \ac{HURDAT2} wind
radii~\citep{demuth2006improvement} showed the highest disagreement for storms
between 2004 and 2015 (Figure~\ref{fig:windcomparison}). The top two maps show
modeled (left) and \ac{HURDAT2} (right) windspeed categorizations for Hurricane
Ike (2008), while the bottom two maps show the same windspeed characterizations
for Hurricane Sandy (2012).  In both cases, the storms were exceptionally large
systems for which high winds persisted well inland from landfall and for which,
based on the \ac{HURDAT2} data, a large number of counties were exposed to
winds of $\ge$34 knots (Figure~\ref{fig:windcomparison}).}
\label{fig:windexamples}
\end{figure}

\begin{figure}[tbhp!]
\centering
\includegraphics[width=0.9\linewidth]{rainexamples}
\caption{Examples of storms where the rain exposure classification method fails
to capture full storm-related rainfall because of the distance constraint used
in that assessment metric. The red line on each map shows the track of the
storm, based on the revised Atlantic hurricane database
\ac{HURDAT2}~\citep{landsea2013}. The color of each county in the map gives the
cumulative precipitation (in millimeters) for that county during the window
from two days before to one day after the storm's closest approach to the
county. The blue outline identifies the collection of counties that were
classified as ``exposed" based on the criteria that the storm passed within
500~\si{\kilo\metre} of the county's population mean center and the cumulative
rainfall was 75 millimeters or more (Table 1 of main text). The map on the left
shows rain-based exposure for Hurricane Ike. For this exceptionally large
storm, there are some counties in northern Texas that received high rainfall
from the storm but are too far from the storm center's track to be classified
as exposed by this metric. The map on the right shows rain-based exposure for
Tropical Storm Lee. For this storm, rain from the storm affected counties in
the Mid-Atlantic and New England as the remnants of the storm moved over those
regions, but storm tracking stopped while the storm was still over the
southeastern part of the \ac{US}, and so these counties are not classified as
exposed to the storm based on this metric.}
\label{fig:rainexamples}
\end{figure}

@@

\bibliography{hurr_exposure}

>>>>

\begin{figure}[tbhp!]
\centering
\includegraphics[width=0.7\linewidth]{hurrtracks}
\caption{Tracks of all tropical cyclones included in the study. The study
included all tracked storms in the revised Atlantic hurricane database
\ac{HURDAT2}~\parencite{landsea2013} that came within 250~\si{\kilo\metre} of at least on
\ac{US} county, 1988\,--\,2015. Thicker lines show the tracks of storms whose
names were retired, indicating that the storm was particularly severe or had
notable impacts~\parencite{retirednames}.}
\label{fig:hurrtracks}
\end{figure}

@@

\begin{figure}[tbhp!]
\centering
\includegraphics[width=\linewidth]{othertopstorms}
\caption{Counties exposed, based on different exposure metrics, to the storms
with largest extent (as measured by the number of counties exposed based on any
metric) from each of the clusters shown in the Jaccard heatmap in the main text
(Figure 2\todo[inline]{Check fig ref}).}
\label{fig:othertopstorms}
\end{figure}

@@

\begin{figure}[tbhp!]
\centering
\includegraphics[width=\linewidth]{windexamples}
\caption{Wind classifications for the two storms, Hurricanes Sandy (2012) and
Ike (2008) for which exposure classifications from modeled wind
data~\parencite{stormwindmodel} and \ac{HURDAT2} wind
radii~\parencite{demuth2006improvement} showed the highest disagreement for storms
between 2004 and 2015 (Figure~\ref{fig:windcomparison}). The top two maps show
modeled (left) and \ac{HURDAT2} (right) windspeed categorizations for Hurricane
Ike (2008), while the bottom two maps show the same windspeed characterizations
for Hurricane Sandy (2012).  In both cases, the storms were exceptionally large
systems for which high winds persisted well inland from landfall and for which,
based on the \ac{HURDAT2} data, a large number of counties were exposed to
winds of $\ge$34 knots (Figure~\ref{fig:windcomparison}\todo[inline]{Fix fig ref}).}
\label{fig:windexamples}
\end{figure}

\begin{figure}[tbhp!]
\centering
\includegraphics[width=0.9\linewidth]{rainexamples}
\caption{Examples of storms where the rain exposure classification method fails
to capture full storm-related rainfall because of the distance constraint used
in that assessment metric. The red line on each map shows the track of the
storm, based on the revised Atlantic hurricane database
\ac{HURDAT2}~\parencite{landsea2013}. The color of each county in the map gives the
cumulative precipitation (in \si{\milli\metre}) for that county during the window
from two days before to one day after the storm's closest approach to the
county. The blue outline identifies the collection of counties that were
classified as ``exposed" based on the criteria that the storm passed within
500~\si{\kilo\metre} of the county's population mean center and the cumulative
rainfall was 75 \si{\milli\metre} or more (Table 1 of main text). The map on the left
shows rain-based exposure for Hurricane Ike. For this exceptionally large
storm, there are some counties in northern Texas that received high rainfall
from the storm but are too far from the storm center's track to be classified
as exposed by this metric. The map on the right shows rain-based exposure for
Tropical Storm Lee. For this storm, rain from the storm affected counties in
the Mid-Atlantic and New England as the remnants of the storm moved over those
regions, but storm tracking stopped while the storm was still over the
southeastern part of the \ac{US}, and so these counties are not classified as
exposed to the storm based on this metric.}
\label{fig:rainexamples}
\end{figure}

@@

\printbibliography

\cleardoublepage

\listoftodos

### 2019-01-28 writing/ehp_abstract.tex
Work some on formatting

\noindent \textbf{Background:} Tropical cyclones bring severe impacts to
\ac{US} communities, including substantial human health risks, from hazards
that include wind, rain, flooding, and tornadoes. However, studies quantifying
tropical cyclone risks and impacts vary widely in how they classify exposure to
tropical cyclones, using various hazard-based metrics and, in some cases, using
distance from the storm track as a surrogate. \\ 
\textbf{Objectives:} (1)~Investigate how well county-level assessments of
tropical cyclone exposure agree when based on distance versus hazard-based
measurements, as well as among assessments based on different hazard
measurements, and (2)~provide software to improve tropical cyclone exposure
assessment for health-related research. \\ 
\textbf{Methods:} We measured county-level exposure to tropical cyclones in the
United States based on distance from the storm track, maximum sustained wind,
rainfall, flooding, and tornadoes for all land-falling or near-land Atlantic
basin storms, for~1996\,--\,2011 for all metrics and up to~1988\,--\,2015 for
specific metrics. We quantified how well county-level exposure assessment
agreed for all pairwise combinations of metrics.\\ 
\textbf{Results:} In most of the storms investigated, agreement in county-level
exposure assessment was at best moderate, and often poor, when using distance
compared with four hazard-based measurements. There was also substantial
disagreement in exposure assessment based on all pairwise combinations of the
four hazard-based measurements. There were geographic patterns in exposures
based on these metrics, with most wind-based exposures near the coast, flood-
and rain-based exposures extending to inland and northern counties, and
tornado-based exposures in southern counties. \\ 
\textbf{Discussion:} Our results suggest that when impact studies use distance
as a surrogate for tropical cyclone exposure, or use one hazard-based metric
when the impact is partly or fully caused by a different hazard, the study will
be prone to exposure misclassification.  To facilitate future research, we make
this multi-hazard storm exposure data available through open-source software. 
\end{abstract}

>>>>

\noindent \textbf{Background:} Tropical cyclones bring severe impacts to
\ac{US} communities, including substantial human health risks, from hazards
that include wind, rain, flooding, and tornadoes. However, studies quantifying
tropical cyclone risks and impacts vary widely in how they classify exposure to
tropical cyclones, using various hazard-based metrics and, in some cases, using
distance from the storm track as a surrogate. \\ 
\textbf{Objectives:} (1)~Investigate how well county-level assessments of
tropical cyclone exposure agree when based on distance versus hazard-based
measurements, as well as among assessments based on different hazard
measurements, and (2)~provide software to improve tropical cyclone exposure
assessment for health-related research. \\ 
\textbf{Methods:} We measured county-level exposure to tropical cyclones in the
\ac{US} based on distance from the storm track, maximum sustained wind,
rainfall, flooding, and tornadoes for all land-falling or near-land Atlantic
basin storms, for~1996\,--\,2011 for all metrics and up to~1988\,--\,2015 for
specific metrics. We quantified how well county-level exposure assessment
agreed for all pairwise combinations of metrics.\\ 
\textbf{Results:} In most of the storms investigated, agreement in county-level
exposure assessment was at best moderate, and often poor, when using distance
compared with four hazard-based measurements. There was also substantial
disagreement in exposure assessment based on all pairwise combinations of the
four hazard-based measurements. There were geographic patterns in exposures
based on these metrics, with most wind-based exposures near the coast, flood-
and rain-based exposures extending to inland and northern counties, and
tornado-based exposures in southern counties. \\ 
\textbf{Discussion:} Our results suggest that when impact studies use distance
as a surrogate for tropical cyclone exposure, or use one hazard-based metric
when the impact is partly or fully caused by a different hazard, the study will
be prone to exposure misclassification.  To facilitate future research, we make
this multi-hazard storm exposure data available through open-source software. 
\end{abstract}

### 2019-01-28 writing/ehp_discussion.tex
Work some on formatting

Distance from a tropical cyclone's track is relatively easy to measure and has
been used as an operational metric of exposure to tropical cyclones in previous
large-scale studies (examples include ...). Since distance itself
does not constitute a hazard, distance is meant in these cases as a surrogate
to capture exposure to hazards from the tropical cyclone. However, here we
found that in assessing \ac{US} county-level exposure to tropical cyclones,
distance is, at best, a moderate, and often a very poor, surrogate for exposure
to the specific tropical cyclone hazards of high wind, extreme rainfall,
flooding, and tornadoes (Figure~\ref{fig:jaccard}).  Therefore, use of distance
to assess tropical cyclone exposure for impact studies could result in
problematic exposure misclassification, which could mask true associations,
even strong associations, between tropical cyclone exposure and outcomes of
interest in impact studies~\citep{savitz2016interpreting, armstrong1998effect}.

In some cases, this exposure misclassification may be differential (i.e.,
associated with the outcome of interest or with factors associated with risk of
the outcome of interest). For example, tropical cyclone wind exposures tend to
be concentrated in counties near the coast, since most tropical cyclones
rapidly decrease in sustained windspeed following landfall. However, tropical
cyclone exposures based on distance can extend well inland, following the
tropical cyclone's tracks, but may not adequately capture all wind-exposed
counties near the coast. In this case, if the etiologically-relevant exposure
is high wind but exposure is classified based on distance, the probability of
being misclassified as unexposed would be higher in coastal counties, while the
probability of being misclassified as exposed would be higher in inland
counties. If coastal counties differ from inland counties in either the outcome
of interest or in factors associated with risk of that outcome, differential
exposure misclassification would exist~\citep{savitz2016interpreting}. Such
differential exposure misclassification can bias estimates of tropical cyclone
effects either towards the null (estimating a lower or null association
compared to the true association that exists) or away from the null (estimating
a larger association than actually exists)~\citep{savitz2016interpreting,
armstrong1998effect}. The use of a single hazard-based metric (e.g., wind)
could cause similar problems if the impact is driven, at least in part, by a
different hazard or by multiple hazards of the tropical cyclone.

Our findings\,---\,that county-level tropical cyclone exposure assessment varies
substantially when different exposure measurements are considered\,---\,aligns with
previous research from atmospheric science and related fields on the
characteristics of tropical cyclones. While tropical cyclone rainfall and
windspeed are often well-correlated when the tropical cyclone is over
water~\citep{cerveny2000}, this relationship often does not remain as strong
once the hurricane has made landfall~\citep{jiang2008}.  Fast-moving tropical
cyclones bring higher risks of dangerous winds inland~\citep{kruk2010}, while
slow-moving tropical cyclone are likely to bring more
rain~\citep{rappaport2000} and cause more damage because of sustained hazardous
conditions~\citep{rezapour2014}. Further, while the likelihood and extent of
flooding during a tropical cyclone is related to the tropical cyclone's
rainfall, it is also driven by factors like top soil saturation and the
structure of the water basin's drainage network~\citep{chen2015, rees2001}.
However, we did find a small set of tropical cyclones for which for which
agreement between metrics were unusually high (e.g., Floyd in~1999, Irene in
2011, Hannah in~2008, Bertha in~1996) For this set of tropical cyclones, the
tropical cyclones' persistent proximity to water may have helped maintain wind
speeds in similar patterns to rain and distance exposures, resulting in this
moderate to good agreement among exposure assessments based on different
metrics.

In our results, wind-based exposure had a strong coastal pattern, with almost
all exposures in counties within about~200~\si{\kilo\metre} (124~mi) of the
coastline. This is consistent with the dramatic decrease in wind intensity that
typically characterizes the landfall of tropical cyclones. Exposures by rain-
and distance-based metrics often extended further inland compared to the
wind-based metric, up to the Appalachian mountains. This agrees with previous
research indicating that the Appalachian mountains' topography both enhances
precipitation during tropical cyclones and provides hydrological conditions for
severe flooding~\citep{rees2001}.  Almost all tornado-based exposures were in
southern coastal states. This pattern echoes previous findings that most
noteworthy tropical cyclone-related tornadoes occur on the right-side of the
tropical cyclone track in Atlantic-basin \ac{US} storms~\citep{moore2012}.

The tropical cyclone exposure averages shown in
Figure~\ref{fig:averageexposure} are limited as estimates of long-term
frequencies, as tropical cyclones follow decadal
patterns~\citep{kossin2007more} likely not adequately captured in the available
data.  However, these frequency maps, together with evidence from specific
tropical cyclones (Figures~\ref{fig:ivanexposure} and~\ref{fig:jaccard}),  do
illustrate the potential for strong differences in spatial patterns in tropical
cyclone exposures, depending on which tropical cyclone hazards are considered.
A few previous studies have sought to determine county-level exposure to
tropical cyclones over multi-year periods, including~\citet{zandbergen2009},
which estimated exposure in \ac{US} counties to all \ac{US} landfalling
Atlantic-basin tropical cyclones between~1851 and~2003, using both a
distance-based metric and a metric that combined distance and windspeed,
and~\citet{kruk2010}, which explored exposure to hurricane-related winds in the
\ac{US}, including inland areas, for~1900\,--\,2008.  Our results suggest that
such exposure assessments may perform well in capturing some tropical cyclone
hazards (e.g., wind), but likely miss other potentially dangerous tropical
cyclone exposures, especially for hazards that repeatedly threaten northern or
inland counties (e.g., rain, flooding).

Dissimilarity in exposure to specific hazards of tropical cyclones can result
in differing patterns in estimates of county-level exposure (Figure~1 [change
to fig. ref]), which can lead to substantial differences in estimates of
population physical exposure (Figure~\ref{fig:topelecdependexposure}), based on
which storm hazard is considered. The measure of a hurricane's intensity, the
Saffir-Simpson scale, expresses intensity as a function of wind speed, and so
fails to capture potential risks from other hazards of the
storm~\citep{smith2009}, and previous assessments of physical exposure to
tropical cyclones have often focused on winds or distance from the storm. For
example, a global study of exposure and vulnerability to natural hazards used a
combination of windspeed above a certain threshold and distance from the
storm's track to assess exposure~\citep{peduzzi2009assessing}. While many storm
impacts might be most strongly linked to wind hazards, there is a growing
recognition of the potential risks of adverse health outcomes and property
damage from rain- and flood-related tropical cyclone hazards in the
\ac{US}~\citep{smith2009}. Such assessments may underemphasize potentially
dangerous exposures to certain regions of the \ac{US}, particularly inland
locations. In fact, based on our assessment of physical exposures to tropical
cyclones among electricity-dependent Medicare beneficiaries, the highest
expected physical exposure under any metric was measured for Philadelphia
County, PA, under the flood metric (Figure~\ref{fig:topelecdependexposure}).
While this county has a similar-sized population of electricity-dependent
Medicare beneficiaries as Miami-Dade County, FL
(Figure~\ref{fig:topelecdependexposure}), the frequency of storm-related flood
events in this inland county results in a very high expected physical exposure
among this subpopulation, while this county is not included in the top ten
counties for physical exposure based on most of the other exposure metrics.

@@

To assist with future tropical cyclone studies, we created and published open
source software to accompany this article~\citep{hurricaneexposuredata,
hurricaneexposure}. Many previous studies have used geographical
information system software (e.g., ArcGIS) to assess exposure to tropical
cyclones in the \ac{US}~\citep{grabich2016, zandbergen2009, czajkowski2011,
kruk2010}. Here, we offer methods to map and output historic exposure to
tropical cyclones that does not require the use of proprietary software but
instead uses a package written in the R statistical programming
language~\citep{R}, which is free and open-source.

In addition to providing tropical cyclone exposure metrics for individual
hazards, this software and data also allow users to create tropical cyclone
exposure profiles based on multiple hazards or craft exposure indices that
combine hazard metrics~\citep{chakraborty2005population, peduzzi2009assessing}.
This ability can be critical, as different hazards of tropical cyclones
often act synergistically in causing impacts~\citep{smith2009}. Further, by
including measurements of different hazard exposures in each county for each
tropical cyclone, this software allows for the development of more complex
exposure indices or models (e.g., random forests, multivariable generalized
linear models) that incorporate multiple tropical cyclone hazard measurements.

In creating this hurricane exposure dataset, we aimed for data that are
reliable, available for all eastern \ac{US} counties, and have no missing data
within available dates. Further, we have investigated how well these data
correspond with data from other available sources (Figures~S7\,--\,11). While
generally in agreement with data from other sources, there are a few
limitations. The wind data are based on modeled, rather than observed, values,
and while the modeled wind data generally agree well with post-analysis maximum
wind radii from \ac{HURDAT2}~\citep{landsea2013} (Figure~S7), for a few
tropical cyclones it did not (e.g., Figure~S10). The rainfall data are from
re-analysis data, which are generally well-correlated with observed
ground-based station data but sometimes oversmooth extreme measurements
(Figure~S8).  The flood and tornado data came from the \ac{NOAA} Storm Events
database, which, while a widely-used database of events maintained by
\ac{NOAA}, is based on reports, and so may be prone to
underreporting~\citep{Ashley2008flood, Curran2000}, especially in less
populated areas~\citep{Witt1998, Ashley2007}, as well as to other reporting
errors. While these are important limitations, we selected these data sources
as among the best currently available for measuring each of these hazards at a
multi-county, multi-year scale.

>>>>

Distance from a tropical cyclone's track is relatively easy to measure and has
been used as an operational metric of exposure to tropical cyclones in previous
large-scale studies (examples include ...). Since distance itself
does not constitute a hazard, distance is meant in these cases as a surrogate
to capture exposure to hazards from the tropical cyclone. However, here we
found that in assessing \ac{US} county-level exposure to tropical cyclones,
distance is, at best, a moderate, and often a very poor, surrogate for exposure
to the specific tropical cyclone hazards of high wind, extreme rainfall,
flooding, and tornadoes (Figure~\ref{fig:jaccard}).  Therefore, use of distance
to assess tropical cyclone exposure for impact studies could result in
problematic exposure misclassification, which could mask true associations,
even strong associations, between tropical cyclone exposure and outcomes of
interest in impact studies~\parencite{savitz2016interpreting, armstrong1998effect}.

In some cases, this exposure misclassification may be differential (i.e.,
associated with the outcome of interest or with factors associated with risk of
the outcome of interest). For example, tropical cyclone wind exposures tend to
be concentrated in counties near the coast, since most tropical cyclones
rapidly decrease in sustained windspeed following landfall. However, tropical
cyclone exposures based on distance can extend well inland, following the
tropical cyclone's tracks, but may not adequately capture all wind-exposed
counties near the coast. In this case, if the etiologically-relevant exposure
is high wind but exposure is classified based on distance, the probability of
being misclassified as unexposed would be higher in coastal counties, while the
probability of being misclassified as exposed would be higher in inland
counties. If coastal counties differ from inland counties in either the outcome
of interest or in factors associated with risk of that outcome, differential
exposure misclassification would exist~\parencite{savitz2016interpreting}. Such
differential exposure misclassification can bias estimates of tropical cyclone
effects either towards the null (estimating a lower or null association
compared to the true association that exists) or away from the null (estimating
a larger association than actually exists)~\parencite{savitz2016interpreting,
armstrong1998effect}. The use of a single hazard-based metric (e.g., wind)
could cause similar problems if the impact is driven, at least in part, by a
different hazard or by multiple hazards of the tropical cyclone.

Our findings\,---\,that county-level tropical cyclone exposure assessment varies
substantially when different exposure measurements are considered\,---\,aligns with
previous research from atmospheric science and related fields on the
characteristics of tropical cyclones. While tropical cyclone rainfall and
windspeed are often well-correlated when the tropical cyclone is over
water~\parencite{cerveny2000}, this relationship often does not remain as strong
once the hurricane has made landfall~\parencite{jiang2008}.  Fast-moving tropical
cyclones bring higher risks of dangerous winds inland~\parencite{kruk2010}, while
slow-moving tropical cyclone are likely to bring more
rain~\parencite{rappaport2000} and cause more damage because of sustained hazardous
conditions~\parencite{rezapour2014}. Further, while the likelihood and extent of
flooding during a tropical cyclone is related to the tropical cyclone's
rainfall, it is also driven by factors like top soil saturation and the
structure of the water basin's drainage network~\parencite{chen2015, rees2001}.
However, we did find a small set of tropical cyclones for which for which
agreement between metrics were unusually high (e.g., Floyd in~1999, Irene in
2011, Hannah in~2008, Bertha in~1996) For this set of tropical cyclones, the
tropical cyclones' persistent proximity to water may have helped maintain wind
speeds in similar patterns to rain and distance exposures, resulting in this
moderate to good agreement among exposure assessments based on different
metrics.

In our results, wind-based exposure had a strong coastal pattern, with almost
all exposures in counties within about~200~\si{\kilo\metre} (124~mi) of the
coastline. This is consistent with the dramatic decrease in wind intensity that
typically characterizes the landfall of tropical cyclones. Exposures by rain-
and distance-based metrics often extended further inland compared to the
wind-based metric, up to the Appalachian mountains. This agrees with previous
research indicating that the Appalachian mountains' topography both enhances
precipitation during tropical cyclones and provides hydrological conditions for
severe flooding~\parencite{rees2001}.  Almost all tornado-based exposures were in
southern coastal states. This pattern echoes previous findings that most
noteworthy tropical cyclone-related tornadoes occur on the right-side of the
tropical cyclone track in Atlantic-basin \ac{US} storms~\parencite{moore2012}.

The tropical cyclone exposure averages shown in
Figure~\ref{fig:averageexposure} are limited as estimates of long-term
frequencies, as tropical cyclones follow decadal
patterns~\parencite{kossin2007more} likely not adequately captured in the available
data.  However, these frequency maps, together with evidence from specific
tropical cyclones (Figures~\ref{fig:ivanexposure} and~\ref{fig:jaccard}),  do
illustrate the potential for strong differences in spatial patterns in tropical
cyclone exposures, depending on which tropical cyclone hazards are considered.
A few previous studies have sought to determine county-level exposure to
tropical cyclones over multi-year periods, including~\textcite{zandbergen2009},
which estimated exposure in \ac{US} counties to all \ac{US} landfalling
Atlantic-basin tropical cyclones between~1851 and~2003, using both a
distance-based metric and a metric that combined distance and windspeed,
and~\textcite{kruk2010}, which explored exposure to hurricane-related winds in the
\ac{US}, including inland areas, for~1900\,--\,2008.  Our results suggest that
such exposure assessments may perform well in capturing some tropical cyclone
hazards (e.g., wind), but likely miss other potentially dangerous tropical
cyclone exposures, especially for hazards that repeatedly threaten northern or
inland counties (e.g., rain, flooding).

Dissimilarity in exposure to specific hazards of tropical cyclones can result
in differing patterns in estimates of county-level exposure
(Figure~1\todo{change to fig. ref}), which can lead to substantial differences
in estimates of population physical exposure
(Figure~\ref{fig:topelecdependexposure}), based on which storm hazard is
considered. The measure of a hurricane's intensity, the Saffir-Simpson scale,
expresses intensity as a function of wind speed, and so fails to capture
potential risks from other hazards of the storm~\parencite{smith2009}, and
previous assessments of physical exposure to tropical cyclones have often
focused on winds or distance from the storm. For example, a global study of
exposure and vulnerability to natural hazards used a combination of windspeed
above a certain threshold and distance from the storm's track to assess
exposure~\parencite{peduzzi2009assessing}. While many storm impacts might be
most strongly linked to wind hazards, there is a growing recognition of the
potential risks of adverse health outcomes and property damage from rain- and
flood-related tropical cyclone hazards in the \ac{US}~\parencite{smith2009}.
Such assessments may underemphasize potentially dangerous exposures to certain
regions of the \ac{US}, particularly inland locations. In fact, based on our
assessment of physical exposures to tropical cyclones among
electricity-dependent Medicare beneficiaries, the highest expected physical
exposure under any metric was measured for Philadelphia County, PA, under the
flood metric (Figure~\ref{fig:topelecdependexposure}).  While this county has a
similar-sized population of electricity-dependent Medicare beneficiaries as
Miami-Dade County, FL (Figure~\ref{fig:topelecdependexposure}), the frequency
of storm-related flood events in this inland county results in a very high
expected physical exposure among this subpopulation, while this county is not
included in the top ten counties for physical exposure based on most of the
other exposure metrics.

@@

To assist with future tropical cyclone studies, we created and published open
source software to accompany this article~\parencite{hurricaneexposuredata,
hurricaneexposure}. Many previous studies have used geographical
information system software (e.g., ArcGIS) to assess exposure to tropical
cyclones in the \ac{US}~\parencite{grabich2016, zandbergen2009, czajkowski2011,
kruk2010}. Here, we offer methods to map and output historic exposure to
tropical cyclones that does not require the use of proprietary software but
instead uses a package written in the R statistical programming
language~\parencite{R}, which is free and open-source.

In addition to providing tropical cyclone exposure metrics for individual
hazards, this software and data also allow users to create tropical cyclone
exposure profiles based on multiple hazards or craft exposure indices that
combine hazard metrics~\parencite{chakraborty2005population, peduzzi2009assessing}.
This ability can be critical, as different hazards of tropical cyclones
often act synergistically in causing impacts~\parencite{smith2009}. Further, by
including measurements of different hazard exposures in each county for each
tropical cyclone, this software allows for the development of more complex
exposure indices or models (e.g., random forests, multivariable generalized
linear models) that incorporate multiple tropical cyclone hazard measurements.

In creating this hurricane exposure dataset, we aimed for data that are
reliable, available for all eastern \ac{US} counties, and have no missing data
within available dates. Further, we have investigated how well these data
correspond with data from other available sources
(Figures~S7\,--\,11\todo{Check fig refs}). While generally in agreement with
data from other sources, there are a few limitations. The wind data are based
on modeled, rather than observed, values, and while the modeled wind data
generally agree well with post-analysis maximum wind radii from
\ac{HURDAT2}~\parencite{landsea2013} (Figure~S7\todo{Check fig refs}), for a
few tropical cyclones it did not (e.g., Figure~S10\todo{Check fig refs}). The
rainfall data are from re-analysis data, which are generally well-correlated
with observed ground-based station data but sometimes oversmooth extreme
measurements (Figure~S8\todo{Check fig refs}).  The flood and tornado data came
from the \ac{NOAA} Storm Events database, which, while a widely-used database
of events maintained by \ac{NOAA}, is based on reports, and so may be prone to
underreporting~\parencite{Ashley2008flood, Curran2000}, especially in less
populated areas~\parencite{Witt1998, Ashley2007}, as well as to other reporting
errors. While these are important limitations, we selected these data sources
as among the best currently available for measuring each of these hazards at a
multi-county, multi-year scale.
